\documentclass[10pt]{article}

\usepackage{url}
% Set up the document per Corrie's design
\usepackage{geometry}
\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}
\setlength{\parindent}{0in}

% #1: Company #2: Date range #3: Company Location  #4: Title #5: Description
\newcommand{\work}[5]{ 
#1\\*
#3\\*
#4\\*
#2\\*
\\*
\makebox[1in][l]{}
\begin{minipage}[t]{5.50in}\small{#5}\end{minipage}
\\
\\
}

\newcommand{\heading}[1]{
#1
\\
}

\newcommand{\address}[1]{
\hfill{}\begin{minipage}[t]{2.00in}#1\end{minipage}
\\
}

\begin{document}
\address{\textbf{Jo\"el Franusic}\\ San Francisco, CA 94117\\ joel@franusic.com}
\\
\\
\\
\heading{EXPERIENCE}

\work{SuperHappyDevHouse}{Nov 2005 - Present}{Bay Area, California}{Co-organizer}{
SuperHappyDevHouse is a monthly hackathon event that combines serious and not-so-serious productivity with a fun and exciting party atmosphere. Primary tasks include welcoming newcomers to the event and interfacing with organizations who host SuperHappyDevHouse (Sun, Google, NASA Ames, etc).
Oversaw the running of the ``Lightning Talks'' up until the 30th SHDH event.
\\
\\
Wrote dynamic name tag layout software in Python and helped design the automated name tag printing system that is used at the event.
}

\work{NetBooks, Inc.}{Jan 2009 - Aug 2009}{San Francisco, California}{System Administrator}{
Worked with a team responsible for the software and external services that ran the ``Working Point'' Ruby on Rails application. Helped to setup, maintain, and manage Capistrano deploy scripts as well as the production infrastructure consisting of Ubuntu, Nginx, Apache, Passenger, git, and related software.
\\
\\
Set up a reliable centralized logging solution for approximately 30 machines using rsyslog, as well as an internal SSL Certificate Authority. Proposed and implemented a backup strategy for corporate and customer data involving encryption of off-site backups, automatic validation of MySQL data, and procedures for restoration of backups in my absence.
\\
\\
Managed the safe handling and destruction of sensitive customer data contained on physical servers as part of a move to Amazon's EC2 platform. Moved sensitive employee data from one law firm to another, under direction of the CEO.
}

\work{PBwiki, Inc.}{Nov 2007 - Jan 2009}{San Mateo, California}{Systems Engineer}{
Implemented OpenID login for PBwiki using JanRain's PHP OpenID library. 
Improved existing Perl deploy scripts to reduce code rollout time from over 10 minutes to under 1 second.
Migrated PBwiki code and servers from PHP4 to PHP5. 
\\
\\
Setup and maintained a reliable office link in the face of unreliable network connectivity. 
Performed a live cutover of the core network switch with no downtime. 
Managed, installed, and removed servers from PBwiki's colocation facility. 
}

\newpage 

\work{Cuesta College}{Nov 2003 - Nov 2007}{San Luis Obispo, California}{Network Technician}{
Provided ``Tier 3'' support for a Community College. 
Duties included server and network troubleshooting, 
as well as installation, maintenance and removal of network equipment.
Also responsible for setup and maintenance of virtual and physical machines as well as server operating systems and software.  
Automated many maintenance tasks using Bash scripting and Perl.
\\
\\ 
Proposed, installed, and promoted the use of MediaWiki - which eventually became the primary source of documentation for the department.
\\
\\
Created and maintained Mac OS X NetBoot images. Managed Mac OS X NetBoot servers and provided technical support for 3 computer labs with a total of roughly 80 machines. Made use of best practices to turn a full time workload into a part time workload.
}

\work{Terracom S.A.R.L.}{Jun 2004 - Sep 2004}{Kigali, Rwanda}{Consultant}{
Gave hands-on training to Terracom staff - topics included: RSA public key encryption, packet sniffing, HTTP proxies, and Symantec Ghost.
\\
\\
Set up and configured a Squid Web Proxy Cache server which increased the apparent capacity of a saturated 3 megabit satellite link and reduced the response time of frequently visited websites from 1000-3000 milliseconds to 10-30 milliseconds.
\\
\\
Worked under the direction of
Albert Butare the Vice Rector at the Kigali Institute of Science and Technology
(now the Rwandan Minister of Energy and Communications) 
to train staff in the use of Symantec Ghost, punch-down methodology, and virus protection. 
Identified and recommended four students to be hired as IT staff by the school.
}

\work{Digital Putty}{Jan 2004 - May 2004}{San Luis Obispo, California}{Customer Service}{
Provided technical support for a wireless ISP with a customer base in the thousands. 
Provided training and assistance to a wide range of computer users. 
Other tasks included on-site assessments for potential wireless customers, network troubleshooting, and maintenance.
}

\work{Synovation, Inc.}{Jan 2002 - Nov 2002}{Modesto, California}{Software Administrator}{
Responsible for modification, maintenance, and support of various in-house software systems 
including a custom Bugzilla installation used for company-wide bug tracking. 
Administration of Sun Netra X1 and E420R systems running Solaris 8. 
Shared administration on various Gnu/Linux 2.4 systems including the corporate webserver.
}

% Citizenship: United States (by birth)

\end{document}
